Inference of Heating Properties from ``Hot'' Non-flaring Plasmas in Active Region Cores II. Nanoflare Trains

### 2016-04-05 hot_non-flaring_plasma_2/hot_non-flaring_plasma_2.tex
removing old figures and includes

	\par\hl{Cut, repeat of Paper 1} An often overlooked consequence of impulsive heating in the corona is electron-ion non-equilibrium. In a fully-ionized hydrogen plasma like the solar corona, interactions between electrons and ions are governed by binary Coulomb collisions. For $n\sim10^9~\mathrm{cm}^{-3}$ and $T\sim10^7~\mathrm{K}$, parameters typical of nanoflare heating, the collisional timescale, $\tau_{ei}=1/\nu_{ei}$, where $\nu_{ei}$ is the Coulomb collision frequency (see \autoref{eq:col_freq}) can be estimated as $\tau_{ei}\approx800$ s. Thus, any heating that occurs on a timescale less than 800 s, such as a nanoflare with a duration of $\tau_H\le100$ s, will result in electron-ion non-equilibrium. Chromospheric evaporation, the response from the transition region to the strong coronal heat flux, does lead to an increase in $n$ and thus a decrease in $\tau_{ei}$. However, we maintain that during this initial phase of impulsive heating, $\tau_{ei}\gg\tau_H$ still holds, with 800 s being an approximate upper bound on $\tau_{ei}$. 
	\par Additionally, while it is often assumed that the electrons are the direct recipients of the prescribed heating function, the degree to which the ions or electrons are preferentially heated in the solar corona is unknown. Thus, it is possible that the ions are preferentially heated, for instance, through ion-cyclotron wave resonances \citep{markovskii_intermittent_2004}. Ion cyclotron waves are excited by plasma instabilities in the lower corona. These waves then propagate upwards through the coronal plasma and wave particle interactions can occur for those ions whose gyrofrequencies have a resonance with the ion-cyclotron wave. Additionally, there is also evidence for ion heating via reconnection, both in laboratory plasmas and in particle-in-cell simulations \citep{ono_ion_1996,yoo_bulk_2014,drake_onset_2014}. Thus, ion heating in the solar corona should not be discounted as a possibility.

@@

		\includegraphics[width=\columnwidth]{figures/heating_event_distributions.pdf}
		\caption{Power-law distributions of heating events for indices $\alpha=-1.5,-2.0,-2.5$ for a given heating frequency, $t_N=5000$ s. For each frequency, $t_N$, we compute $N_R$ runs such that the total number of events simulated for each $t_N$ is $N\times N_R\sim10^4$.}
		\label{fig:event_dist}

@@

@@

@@

	\subsection{Separate Electron and Ion Heating}
	\label{subsec:electron_ion_heating}

@@

		\begin{minipage}[c]{0.49\textwidth}
			\subfigure{%
			\includegraphics[width=\columnwidth]{figures/{ebtel_L40.0_tpulse100.0_alpha2.5-b1.0_electron_heating_dem}.pdf}
			\label{fig:el_em_curves}}
		\end{minipage}
		\begin{minipage}[c]{0.49\textwidth}
			\subfigure{%
			\includegraphics[width=\columnwidth]{figures/{ebtel_L40.0_tpulse100.0_alpha2.5-b1.0_electron_heating_hs_compare}.pdf}
			\label{fig:el_em_slopes}}
			\subfigure{%
			\includegraphics[width=\columnwidth]{figures/{ebtel_L40.0_tpulse100.0_alpha2.5-b1.0_electron_heating_dem_derivs}.pdf}
			\label{fig:el_em_derivs}}
		\end{minipage}
		\caption{$\alpha=-2.5,~\beta=1,~L=40$ Mm, electron heating. \textbf{Left:} $\log{\mathrm{EM}}$ as a function of $\log{T}$ for all values of $t_N$. There is an artificial spacing of $\Delta\log{\mathrm{EM}}=0.2$ between each curve. The bold blue (red) lines on either side of the peak show the linear fit to the cool (hot) emission. \textbf{Top right:} Average slopes from power-law fits to all $N_{R}$ curves as a function of $t_N$. The error bars indicate one standard deviation from the distribution of $N_{R}$ fits. In the case of hot slopes, the absolute value is shown. The dashed, solid, and dot-dashed reference lines are placed at 2, 3, and 5 respectively. \textbf{Bottom right:} Derivative of $\log{\mathrm{EM}}$ with respect to $\log{T}$. The dotted reference lines are placed at -5.5, -2.5, 2, and 3. The legend is the same as the left panel.}

@@

		\begin{minipage}[c]{0.49\textwidth}
			\subfigure{%
			\includegraphics[width=\columnwidth]{figures/{ebtel_L40.0_tpulse100.0_alpha2.5-b1.0_ion_heating_dem}.pdf}
			\label{fig:ion_em_curves}}
		\end{minipage}
		\begin{minipage}[c]{0.49\textwidth}
			\subfigure{%
			\includegraphics[width=\columnwidth]{figures/{ebtel_L40.0_tpulse100.0_alpha2.5-b1.0_ion_heating_hs_compare}.pdf}
			\label{fig:ion_em_slopes}}
			\subfigure{%
			\includegraphics[width=\columnwidth]{figures/{ebtel_L40.0_tpulse100.0_alpha2.5-b1.0_ion_heating_dem_derivs}.pdf}
			\label{fig:ion_em_derivs}}
		\end{minipage}
		\caption{Same as \autoref{fig:el_em}, but for the case in which all of the heating is given to the ions.}

@@

	\subsection{Single-fluid}
	\label{subsec:single_heating}

@@

		\begin{minipage}[c]{0.49\textwidth}
			\subfigure{%
			\includegraphics[width=\columnwidth]{figures/{ebtel_L40.0_tpulse100.0_alpha2.5-b1.0_single_heating_dem}.pdf}
			\label{fig:single_em_curves}}
		\end{minipage}
		\begin{minipage}[c]{0.49\textwidth}
			\subfigure{%
			\includegraphics[width=\columnwidth]{figures/{ebtel_L40.0_tpulse100.0_alpha2.5-b1.0_single_heating_hs_compare}.pdf}
			\label{fig:single_em_slopes}}
			\subfigure{%
			\includegraphics[width=\columnwidth]{figures/{ebtel_L40.0_tpulse100.0_alpha2.5-b1.0_single_heating_dem_derivs}.pdf}
			\label{fig:single_em_derivs}}
		\end{minipage}
		\caption{Same as \autoref{fig:el_em}, but for the single-fluid case in which electron-ion equilibrium is assumed.}
		\label{fig:single_em}

@@

	\label{subsec:non-eq_ion}

@@

		\begin{minipage}[c]{0.49\textwidth}
		\end{minipage}
		\begin{minipage}[c]{0.49\textwidth}
		\end{minipage}
			\caption{Figures for the cases of non-equilibrium ionization.}
			\label{fig:teff_test_case}

@@

	\subsection{Full Parameter Space Comparison}
	\label{subsec:all_params}

@@

		\begin{minipage}[c]{0.49\textwidth}
			\subfigure{%
			\includegraphics[width=\columnwidth]{figures/{el_cool_alpha_histo}.pdf}
			\label{fig:el_cool_alpha_histo}}
			\subfigure{%
			\includegraphics[width=\columnwidth]{figures/{el_hot_tn_histo}.pdf}
			\label{fig:el_hot_tn_histo}}
		\end{minipage}
		\begin{minipage}[c]{0.49\textwidth}
			\subfigure{%
			\includegraphics[width=\columnwidth]{figures/{ion_cool_alpha_histo}.pdf}
			\label{fig:ion_cool_alpha_histo}}
			\subfigure{%
			\includegraphics[width=\columnwidth]{figures/{single_hot_tn_histo}.pdf}
			\label{fig:single_cool_tn_histo}}
		\end{minipage}
			\caption{Histograms of emission measure slopes from the entire parameter space as described in \autoref{fig:parameter_space}. \textbf{Top left:} cool slopes grouped by heating function for the electron heating case; \textbf{Top right:} cool slopes grouped by heating function for the ion heating case; \textbf{Bottom left:} hot slopes grouped by $t_N$ for the electron heating case; \textbf{Bottom right:} hot slopes grouped by $t_N$ value for the single-fluid case. In the cases where the slopes are grouped by $t_N$, only $T_N=1000,2000,3000,4000,5000$ s are shown for aesthetic purposes.}

>>>>

@@

@@

	\label{subsec:heating_stats}

@@

	\label{subsec:nei}
	\par When considering the role of nanoflares in the production of hot plasma in AR cores, it is important to take non-equilibrium ionization (NEI) into account \citep{bradshaw_explosive_2006,reale_nonequilibrium_2008}. In a steady heating scenario, the ionization state is an adequate measure of the electron plasma temperature. Because the heating timescale is long (effectively infinite), the ionization state has plenty of time to come into equilibrium with the electron temperature. 
	\par In a nanoflare train, when the heating frequency is high, the loop is not allowed to drain or cool sufficiently between events, meaning the ionization state is kept at or near equilibrium. However, as the heating frequency decreases, the loop is allowed to cool and drain more and more during the inter-event period. If the heating occurs on a short enough timescale, the ionization state will not be able to reach equilibrium with the electron plasma before the loop undergoes rapid cooling by thermal conduction. Furthermore, if the frequency is sufficiently low so as to allow the loop to drain during the inter-event period, the ionization equilibrium timescale will increase. Thus, in the context of intermediate- to low-frequency nanoflares, NEI should be considered.
	\par As in \citetalias{barnes_inference_2016}, we use the numerical code\footnote{This code has been made freely available by the author and can be downloaded at: https://github.com/rice-solar-physics/IonPopSolver} outlined in \citet{bradshaw_numerical_2009} to compute the non-equilibrium ionization states and the corresponding effective electron temperature, $T_{eff}$ that would be inferred by assuming ionization equilibrium. Using $T_eff$, we are then able to compute a corresponding NEI emission measure distribution.

@@

	\subsection{Emission Measure Distributions}

@@

		\caption{EM grids will go here, electron heating}

@@

		\caption{EM grids will go here, ion heating}

@@

	\subsection{Pre-nanoflare Density}
	\label{subsec:pre_nanoflare_density}

@@

		\caption{\hl{Maybe single EM grid will go here}}

@@

	\subsection{Hot Plasma Diagnostics}
	\label{subsec:diagnostics}

@@

		\caption{Diagnostics figures}

@@

	%\subsection{Full Parameter Space Comparison}
	%\label{subsec:all_params}

@@

		\caption{\hl{Put EM ratio histograms here, maybe include hot slope histograms somewhere too}}
